### 2013-05-24 inst/examples/BUGS/parametric-vs-nonparametric.Rmd
parallel jags working now

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <- K # observations start from
x0 <- Xo # simulation under policy starts from
Tobs <- 40
```

@@

```{r obs, dependson="sdp-pars"}
  set.seed(1234)
  #harvest <- sort(rep(seq(0, .5, length=7), 5))
  x <- numeric(Tobs)
  x[1] <- 2
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)
  obs <- data.frame(x = c(rep(0,nz), 
                          pmax(rep(0,Tobs-1), x[1:(Tobs-1)])), 
                    y = c(rep(0,nz), 
                          x[2:Tobs]))
raw_plot <- ggplot(data.frame(time = 1:Tobs, x=x), aes(time,x)) + geom_line()
raw_plot
```

@@

# Can give a list of starting values or a function that can create random values 
jags.inits <- function(){
  list("K"=init_p["K"] * rlnorm(1,0,.5),
       "logr0"=log(init_p["r0"]) * rlnorm(1,0,.5),
       "logtheta"=log(init_p["theta"]) * rlnorm(1,0,.5), 
       "stdQ"=sqrt(0.05) * rlnorm(1,0,.5),
       "stdR"=sqrt(0.1) * rlnorm(1,0,.5),
       "x"=y,
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

set.seed(12345)
# parallel refuses to take variables as arguments (e.g. n.iter = 1e5 works, but n.iter = n doesn't)
allen_jags <- jags(data=jags.data, inits=jags.inits, jags.params, n.chains=n.chains, 
                n.iter=n.iter, n.thin=n.thin, n.burnin=n.burnin, 
                model.file="allen.bugs", progress="none")

#Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
allen_jags <- autojags(allen_jags, n.update=10, n.iter=n.iter, 
                       n.thin = n.thin, progress="none") 
```

#### Convergence diagnostics for parametric bayes

>>>>

```{r sdp-pars, dependson="stateeq"}
sigma_g <- 0.05
sigma_m <- 0.0
z_g <- function() rlnorm(1, 0, sigma_g)
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
x_grid <- seq(0, 1.5 * K, length=50)
h_grid <- x_grid
profit <- function(x,h) pmin(x, h)
delta <- 0.01
OptTime <- 50  # stationarity with unstable models is tricky thing
reward <- 0
xT <- 0
Xo <-  allee+.5# observations start from
x0 <- K # simulation under policy starts from
Tobs <- 40
```

@@

```{r obs, dependson="sdp-pars"}
  set.seed(1234)
  #harvest <- sort(rep(seq(0, .5, length=7), 5))
  x <- numeric(Tobs)
  x[1] <- Xo
  nz <- 1
  for(t in 1:(Tobs-1))
    x[t+1] = z_g() * f(x[t], h=0, p=p)
  obs <- data.frame(x = c(rep(0,nz), 
                          pmax(rep(0,Tobs-1), x[1:(Tobs-1)])), 
                    y = c(rep(0,nz), 
                          x[2:Tobs]))
raw_plot <- ggplot(data.frame(time = 1:Tobs, x=x), aes(time,x)) + geom_line()
raw_plot
```

@@

# Can give a list of starting values or a function that can create random values

jags.inits <- function(){
  init_p = c(1, 10, 2)
  names(init_p) = c("r0", "K", "theta")
  list("K"=init_p["K"] * rlnorm(1,0,.1),
       "logr0"=log(init_p["r0"]) * rlnorm(1,0,.1),
       "logtheta"=log(init_p["theta"]) * rlnorm(1,0,.1), 
       "stdQ"=sqrt(0.05) * rlnorm(1,0,.1),
       "stdR"=sqrt(0.1) * rlnorm(1,0,.1),
       "x"=y,        
       .RNG.name="base::Wichmann-Hill", .RNG.seed=123)
}

set.seed(1234)
# parallel refuses to take variables as arguments (e.g. n.iter = 1e5 works, but n.iter = n doesn't)
allen_jags <- do.call(jags.parallel, list(data=jags.data, inits=jags.inits, 
                                          jags.params, n.chains=n.chains, 
                                          n.iter=n.iter, n.thin=n.thin, 
                                          n.burnin=n.burnin, model.file="allen.bugs"))

#Run again iteratively if we haven't met the Gelman-Rubin convergence criterion
recompile(allen_jags) # required for parallel
allen_jags <- do.call(autojags, list(object=allen_jags, n.update=10, 
                                     n.iter=n.iter, n.thin = n.thin))
```

#### Convergence diagnostics for Allen model
